---
title: "clinical data practice"
output: 
 html_document:
   theme: lumen
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output/") })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

> This practice works on a dataset of the following research:    
> [doi:10.1016/j.nutres.2018.12.004](https://doi.org/10.1016/j.nutres.2018.12.004)    


This research tested the effect of ingesting encapsulated lipid beads on subsequent food intake of overweight adults. The experiment adopted a randomized placebo-controlled crossover design.   

|        Two groups of adults were treated with either yogurt containing 
|        encapsulated lipid beads (**active group**) or yogurt with 
|        non-encapsulated nutrient (**placebo/control group**) before
|        an ad libitum pasta meal. After a week of washout period, each
|        of the two subject groups was treated with one of the other 
|        experimental treatment. The experiment data can be found on 
|        [Mendeley Data](https://data.mendeley.com/datasets/hxyx3vdf3b/1).    

### Load cleaned datasets
```{r results="hide", message=FALSE}
source ("./clinical_data_practice.R")
```

### Overview of datasets    
##### The first dataset contains basic subject description and food consumption. The calories of pasta consumed by the subjects in each *ad libtum* session were recorded after each treatment. Each subject experienced 2 treatments, in different order, across 2 time points. Therefore, each subject generated 2 data points, the calories taken after an active treatment (**activeIntake_kcal**), and those after a control treatment (**controlIntake_kcal**).  
```{r collapse=TRUE}
str (dat1)
```

##### The second dataset contains measurements of subject satiaty and unpleasant GI symptoms
```{r collapse=TRUE}
str (dat2)
```
    
### First research question: do subjects treated with encapsulated lipid beads consume less food than subjects treated with non-encapsulated beads?    
    
##### Paired-t test was used to comapare controlIntake_kcal and activeIntake_kcal    
```{r}
ttest <- t.test (x = dat1$controlIntake_kcal, y = dat1$activeIntake_kcal, paired = TRUE)

ttest$p.value
```

##### The answer is yes. Subjects' consumption is significantly lower in active treatment than that in control treatment.
```{r fig.height=4, fig.width=4}
library (ggplot2)
dat1p <- dat1 %>% 
  select (controlIntake_kcal, activeIntake_kcal) %>% 
  gather (key = key, value = value) %>% 
  group_by (key) %>% 
  summarise (mean = mean(value),
             sem = sd(value)/sqrt(length(value)))

ggplot (dat1p, aes (x = key, y = mean, fill = key)) +
  geom_bar (stat = "identity", width = 1, position ="dodge", aes (color = key, fill = key)) +
  geom_linerange (aes (ymin = mean - sem, ymax = mean + sem)) +
  scale_color_manual (values = c ("activeIntake_kcal" = "black", "controlIntake_kcal" = "grey50")) +
  scale_fill_manual (values = c ("activeIntake_kcal" = "black", "controlIntake_kcal" = "grey90")) +
  scale_x_discrete(expand = c(0.6,0.6), labels = c ("activeIntake_kcal" = "Active", "controlIntake_kcal" = "Cnotrol")) +
  scale_y_continuous (limits = c(0, 1000)) +
  labs (x = "", y = "Food intake (kcal)") +
  theme_classic () +
  theme (legend.position = "none")
```

### The second question asks whether subjects in active treatment have more desire to eat than in control treatment.
```{r fig.height = 8, fig.width=6}
dat2p <- dat2 %>% 
  select (Time,
          `Satiety-active`, `Satiety-control`, "Fullness-active", "Fullness-control", 
          "Hunger-active", "Hunger-control", `Desire.to.eat-active`, `Desire.to.eat-control`, 
          `Desire.to.snack-active`, `Desire.to.snack-control`) %>% 
  filter (Time >= 90) %>% 
  gather (key, value, -Time) %>% 
  separate(key, c("var", "group"), "-") %>% 
  group_by(var, group, Time) %>% 
  summarize (mean = mean (value),
             sem = sd(value)/sqrt(length(value)))

multiPlot <- function (data, title){
  
  ggplot (data, aes (x = Time, y = mean, group = group)) +
    geom_linerange (aes (ymin = mean - sem, ymax = mean + sem)) +
    geom_line (aes (color = group)) +
    geom_point (shape = 21, aes (color = group, fill = group)) +
    scale_color_manual(values = c("active" = "black", "control" = "grey"))+
    scale_fill_manual (values = c("active" = "black", "control" = "white")) +
    labs (x = "Time (min)", y = "VAS score (mm)") +
    scale_y_continuous(limits = c(0,100)) +
    ggtitle (title) +
    theme_classic()+
    theme(legend.position='none', 
          plot.title = element_text(hjust = 0.05, vjust = -8)) 

  }
#multiPlot ("Satiety", "A")
A <- multiPlot (dat2p %>% filter (var == "Satiety"), "A")
B <- multiPlot (dat2p %>% filter (var == "Fullness"), "B")
C <- multiPlot (dat2p %>% filter (var == "Hunger"), "C")
D <- multiPlot (dat2p %>% filter (var == "Desire.to.eat"), "D") 
E <- multiPlot (dat2p %>% filter (var == "Desire.to.snack"), "E")

library (gridExtra)
grid.arrange (A,B,C,D,E)
```

```{r fig.width = 5, fig.height = 4}
library (pracma)
datAUC <- dat2 %>%
  select (ID, Time,
          `Satiety-active`, `Satiety-control`, "Fullness-active", "Fullness-control", 
          "Hunger-active", "Hunger-control", `Desire.to.eat-active`, `Desire.to.eat-control`, 
          `Desire.to.snack-active`, `Desire.to.snack-control`) %>% 
  filter (Time >= 90) %>% 
  gather (key, value, -ID, -Time) %>% 
  separate (key, c("var", "group"), "-") %>% 
  group_by (ID, var, group) %>% 
  summarize (auc = trapz (Time, value))

dat3p <- datAUC %>% 
  group_by(var, group) %>% 
  summarize (mean = mean (auc),
             sem = sd(auc)/sqrt (length(auc)))


level_order <- factor (dat3p$var, levels = c("Satiety", "Hunger", "Desire.to.eat", "Desire.to.snack", "Fullness"))

ggplot (dat3p, aes (x = level_order, y = mean, group = group, fill = group)) +
  geom_linerange (position = position_dodge(width = 0.7),aes (ymin = mean - sem, ymax = mean + sem)) +
  geom_bar (stat = "identity", position = position_dodge(), aes(color = group)) +
  scale_color_manual (values = c("black", "grey50")) +
  scale_fill_manual (values = c("black", "grey90")) +
  scale_x_discrete (labels = c ("Satiety", "Hunger", "Desire \nto eat", "Desire \nto snack", "Fullness")) +
  scale_y_continuous(limits = c(0,6000), breaks = c (1000, 2000, 3000, 4000, 5000, 6000), labels = c ("", 2000, "", 4000, "", 6000)) +
  labs (x = "", y = "AUC VAS (mm.min)") +
  theme_classic()
```

```{r results="hold"}
datAUC <- datAUC %>% 
  spread (group, auc) %>% 
  arrange (desc(var))

t.test (x = datAUC$control [which (datAUC$var == "Satiety")], y = datAUC$active [which (datAUC$var == "Satiety")], paired = TRUE)

t.test (x = datAUC$control [which (datAUC$var == "Hunger")], y = datAUC$active [which (datAUC$var == "Hunger")], paired = TRUE)

t.test (x = datAUC$control [which (datAUC$var == "Desire.to.eat")], y = datAUC$active [which (datAUC$var == "Desire.to.eat")], paired = TRUE)

t.test (x = datAUC$control [which (datAUC$var == "Desire.to.snack")], y = datAUC$active [which (datAUC$var == "Desire.to.snack")], paired = TRUE)

t.test (x = datAUC$control [which (datAUC$var == "Fullness")], y = datAUC$active [which (datAUC$var == "Fullness")], paired = TRUE)
```
##### No, the levels of satiety, hunger, desire to eat, desire to snack, or fullness did not differ significantly between treatments    
    
```{r fig.height=6, fig.width=6}
datAUC <- dat2 %>%
  select (ID, Time,
          `Satiety-active`, `Satiety-control`, "Fullness-active", "Fullness-control", 
          "Hunger-active", "Hunger-control", `Desire.to.eat-active`, `Desire.to.eat-control`, 
          `Desire.to.snack-active`, `Desire.to.snack-control`) %>% 
  filter (Time >= 90) %>% 
  gather (key, value, -ID, -Time) %>% 
  separate (key, c("var", "group"), "-") %>% 
  group_by (ID, var, group) %>% 
  summarize (auc = trapz (Time, value))


dat4p <- dat2 %>% 
  select (Time, 
          `Bloating-active`, `Bloating-control`,
          `Discomfort-active`, `Discomfort-control`,
          `Pain-active`, `Pain-control`,
          `Nausea-active`, `Nausea-control`) %>% 
  filter (Time >= 90) %>% 
  gather (key, value, -Time) %>% 
  separate(key, c("var", "group"), "-") %>% 
  group_by(var, group, Time) %>% 
  summarize (mean = mean (value),
             sem = sd(value)/sqrt(length(value)))

A <- multiPlot (dat4p %>% filter (var == "Bloating"), "A")
B <- multiPlot (dat4p %>% filter (var == "Discomfort"), "B")
C <- multiPlot (dat4p %>% filter (var == "Pain"), "C")
D <- multiPlot (dat4p %>% filter (var == "Nausea"), "D") 

grid.arrange(A,B,C,D)
```

```{r results="hold"}
datAUC <- dat2 %>% 
   select (ID, Time, 
          `Bloating-active`, `Bloating-control`,
          `Discomfort-active`, `Discomfort-control`,
          `Pain-active`, `Pain-control`,
          `Nausea-active`, `Nausea-control`) %>% 
  filter (Time >= 90) %>% 
  gather (key, value, -ID, -Time) %>% 
  separate (key, c("var", "group"), "-") %>% 
  group_by (ID, var, group) %>% 
  summarize (auc = trapz (Time, value)) %>% 
  spread (group, auc) %>% 
  arrange (var)

wilcox.test (x = datAUC$control [which (datAUC$var == "Bloating")], y = datAUC$active [which (datAUC$var == "Bloating")], paired = TRUE)

wilcox.test (x = datAUC$control [which (datAUC$var == "Discomfort")], y = datAUC$active [which (datAUC$var == "Discomfort")], paired = TRUE)

wilcox.test (x = datAUC$control [which (datAUC$var == "Pain")], y = datAUC$active [which (datAUC$var == "Pain")], paired = TRUE)

wilcox.test (x = datAUC$control [which (datAUC$var == "Nausea")], y = datAUC$active [which (datAUC$var == "Nausea")], paired = TRUE)

```
    
##### None of the GI symptoms differed significantly between groups    
    
|
|