---
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: sandstone
    hightlight: haddock
    code_folding: hide
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output/") })
---

```{r, echo = FALSE}
knitr::opts_chunk$set (comment="##", fig.path = "../images/", warning = FALSE)
```

## Web scraping: data extraction and transformation
 * Extract information from webpages
 * Transform the information into tidy data table
 * Visualize the data    
    
```{r message=FALSE, warning=FALSE}
library (rvest); library (httr)
library (tidyverse); library (ggplot2); library (lubridate)
library (maps); library (mapdata); library (ggmap)
library (RColorBrewer)
```

### 1-- Example webpage 1:   
this page shows the contact information of several work sites of the organization    

 * Extract the information using GET method    
 * Plot the location information onto a map   
     
```{r}
url = "https://www.twbiobank.org.tw/new_web/contact.php"
res = GET (url) # use GET method to get the web response
res

# An overview of the web response
str (res)  
# res$content # information we want is usually in the content section
              # but the content is usually binary coded
```

### 2-- Extract the work site addresses we want from the content
```{r}
address <- res %>% 
  content (as = "text") %>% 
  read_html %>% 
  html_nodes (xpath = "//div[@class='panel address']") %>% 
  html_text %>% # turn the content into text
  as.data.frame # turn the table into data.frame

#str(address)
head (address) # Overview of the scraped content
```

#### Some data cleaning:    
divide the location string into the following columns, city, site, address, and building    
    
```{r}
address_df <- address %>% 
  separate (".", into = c ("city", "location"), sep = 2) %>% 
  slice (2:n()) # select 2nd to n rows

for (i in 1:nrow(address_df))
{
  address_df$location[i] <- 
    ifelse (grepl("駐站", address_df$location[i]) == FALSE, 
            sub ("醫院", "醫院駐站", address_df$location[i]), address_df$location[i])
}

address_df <- address_df %>% 
  mutate (site = sub ("駐站.*", "", address_df$location),
          address = sub ("^.*駐站", "", address_df$location)) %>% 
  separate ("address", into = c ("address", "building"), sep = " ") %>% 
  select (-location) %>% 
  mutate (type = "cohort") 

address_df$type[32:38] <- "medical_center"
  
address_df$address[31] <- sub (".*)", "", address_df$address[31])

head (address_df)
```

### 3-- Extract the coordinate of the sites from the content
```{r}
geo <- res %>% 
  content (as = "text") %>% 
  read_html %>% 
  html_nodes (xpath = "//li[@data-geo-lat]") %>% 
  html_attrs 
```

#### Some data cleaning:    
turn the list into data frame and rename columns    
    
```{r}
geo_df <- t (as.data.frame (geo, col.names = paste0("X", c(1:34)))) 
geo_df <- as.data.frame(geo_df)
head (geo_df)

colnames (geo_df) <- c("lat", "long")
row.names (geo_df) <- NULL
```

### 4-- Combine the 2 tables: site addresses and coordinates
```{r}
stations <- cbind (address_df, geo_df) 
library (knitr); library (kableExtra)
kable (stations, format = "html") %>% 
  kable_styling(bootstrap_options = "striped", font_size = 12) %>%
  scroll_box(height = "300px")
```

### 5-- Plot the sites     
 * mouse over to see site names   
 * Reference: [save leaflet map as png images](https://stackoverflow.com/a/34672309)
    
```{r}
stations$lat <- as.numeric (as.character (stations$lat))
stations$long <- as.numeric (as.character (stations$long))
#tw <- map_data("world2")[which(map_data("world2")$region == "Taiwan"),]

library(leaflet)
(m <-
leaflet() %>% addProviderTiles(providers$Stamen.TonerLite) %>% 
  setView (lng = 121, lat = 23.5, zoom = 7) %>% 
  addCircles(data = stations %>% filter (type=="cohort"), 
             color = brewer.pal(3, "YlGnBu")[3], weight = 5, opacity = 1,
             lng = ~long, lat = ~lat, label = ~site) %>%
  addCircles(data = stations %>% filter (type=="medical_center"), 
             color = brewer.pal(3, "Reds")[3], weight = 5, opacity = 1,
             lng = ~long, lat = ~lat, label = ~site) 
)

library(mapview)
mapshot(m, file = "../images/worksite_loc.png")
```


### 6-- Example webpage 2:    
the recruitment situation of each sites     

 * Extract information using POST method    
 * Plot the recruitment outcome onto the map    
     
```{r}
url <- "https://www.twbiobank.org.tw/TBB/COHORT/to/site_excel_preview"
today <- today()
postData <- list (start_date = "",
                  end_date = today)
res <- POST (url, body = postData, encode = "form") 
text <- res %>% 
  content (as = "text")

# View the first part of the scraped content, which is a string
substr (text, 1, 300)
```

#### Clean up the string a bit
 * Reference: [remove brackets from strings](https://stackoverflow.com/a/17528237)    
    
```{r}
# Remove the square brackets ([{ }]) at the beginning and end of the string
text2 <- gsub("^\\[\\{|\\}\\]$", "",text) 

# Remove all quotation marks
text3 <- gsub('\\"', "", text2)

# Take a look at the cleanning so far
substr (text3, 1, 300)
```

#### Transform the string into a table
```{r}
# Split the string by the left curly brackets ({)
split1 <- strsplit (text3, '},\\{')[[1]] %>% as.data.frame
colnames (split1) <- "col"
head (split1)

# Further separate the content into columns
split2 <- separate (split1, col, into = paste0("v", 1:10), sep =",")
head (split2)

# Remove the part before the semicolons
split3 <- apply (split2, 2, function(x) gsub ("^.+:(.)", "\\1", x)) %>% 
  as.data.frame (stringsAsFactors = FALSE)
head (split3)

# Rename and reorder the columns
names <- c ("駐站","尚未聯絡","聯絡中","聯絡總計","預約中","已收案","已結案","收案總計","補件","新增聯絡")
colnames (split3) <- names
baseline <- split3 %>% 
  select (駐站, 新增聯絡, everything()) %>% 
  mutate (recruitStatus = 0) # add this column so I can combine with the followup table later

```


### 7-- Repeat the extraction and transformation process for follow-up recruitment{.tabset}
#### Baseline
```{r}
kable (baseline, "html") %>% 
  kable_styling(bootstrap_options = "striped", font_size = 12)
```
#### Follow-up
```{r}
url <- "https://www.twbiobank.org.tw/TBB/COHORT/to/site_excel_preview_follow"
postData <- list (start_date = "",
                  end_date = today)
res <- POST (url, body = postData, encode = "form") 
text <- res %>% 
  content (as = "text")

# Remove the square brackets ([ ]) at the beginning and end of the string
text2 <- gsub("^\\[\\{|\\}\\]$", "",text) 
# Remove all quotation marks
text3 <- gsub('\\"', "", text2)

# Split the string by the left curly brackets ({)
split1 <- strsplit (text3, '},\\{')[[1]] %>% as.data.frame
colnames (split1) <- "col"

# Further separate the content into columns
split2 <- separate (split1, col, into = paste0 ("v", 1:10), sep = ",")

# Remove the part before the semicolons
split3 <- apply (split2, 2, function(x) gsub ("^.+:(.)", "\\1", x)) %>% 
  as.data.frame (stringsAsFactors = FALSE)

# Rename and reorder the columns
names <- c ("駐站","尚未聯絡","聯絡中","聯絡總計","預約中","已收案","已結案","收案總計","補件","新增聯絡")
colnames(split3) <- names
followup <- split3 %>% 
  select (駐站, 新增聯絡, everything()) %>% 
  mutate (recruitStatus = 1)

kable (followup, "html") %>% 
  kable_styling (bootstrap_options = "striped", font_size = 12)
```


### 8-- Combine the baseline and followup table and make a bar plot
```{r fig.width=10, fig.height=6}
table <- rbind (baseline, followup) %>% 
  mutate (收案總計 = as.numeric (as.character (收案總計)),
              recruitStatus = as.character (recruitStatus), 
              levels = 1:n()) 
ggplot (table, aes (x = fct_reorder (駐站, desc(levels)), 
                    y = as.numeric(收案總計), 
                    fill = fct_relevel (recruitStatus, "1"))) +
  geom_bar (stat = "identity") +
  theme_minimal() +
  theme(text = element_text (family="STHeiti"),
        legend.position = "top", legend.direction = "horizontal") +
  labs (x = "", y = "收案總計(人)") +
  scale_fill_brewer (name = "recruitment status", 
                     labels = c("follow-up", "baseline"), 
                     palette = "YlGnBu") +
  coord_flip()
```

### 9-- show the density on the map
```{r fig.height=10}
df <-  cbind (as.character(baseline$駐站),  stations$site) %>% 
  as.data.frame (stringsAsFactors = FALSE)
names (df) <- c ("names_tbb", "names_web")
df[35:38, 1] <- NA
df[32:38, 2] <- NA

st <- c("宏恩", "北護", "汀州", "馬偕", "耕莘", 
        "雙和", "輔", "桃園", "新竹", "苗栗", 
        "醫藥", "豐原", "澄清", "化醫", "秀傳", 
        "員生", "埔里", "大林", "朴子", "義醫", 
        "義基", "新營", "南市", "柳營", "民生", 
        "義大", "大同", "小港", "屏東", "羅東", 
        "門諾", "臺東", "澎湖", "金門")

for (i in 1:length(df$names_tbb)){
  ifelse (grepl(st[i], df$names_web), 
  baseline$names_web[i] <- df$names_web[grepl(st[i], df$names_web)], NA )
}

baseline$long <- stations$long [match (baseline$names_web, stations$site)]
baseline$lat <- stations$lat [match (baseline$names_web, stations$site)]
baseline [c(2,5,6,14,16,21), "long"] <- c (121.50356599999998, 
                                           121.53573989999995,
                                           121.49352599999997,
                                           120.52717810000001, 
                                           120.566371,
                                           120.45107759999996)
baseline [c(2,5,6,14,16,21), "lat"] <- c (25.041664,
                                          24.976294,
                                          24.992699,
                                          23.9506679,
                                          23.959309,
                                          23.4999232)

pal <- colorNumeric (
  palette = "Blues",
  domain = as.numeric (as.character(baseline$收案總計)))
leaflet() %>% 
  addProviderTiles(providers$Stamen.TonerLite) %>% 
  setView (lng = 121, lat = 23.5, zoom = 8) %>%
  addCircles (data = baseline,
             # color = ~pal (as.numeric (as.character (收案總計))),
             color = brewer.pal(3, "YlGnBu")[3],
             opacity = 1, fillOpacity = 0.3, weight = 3,
             lng = ~long, lat = ~lat, label = ~駐站,
             radius = ~2*as.numeric (as.character (收案總計))) #%>%
  
  # addLegend (data = baseline,
  #   pal = pal, values = ~as.numeric (as.character (baseline$收案總計)),
  #   title = "baseline recruitment (people)",
  #   #labFormat = labelFormat(prefix = "$"),
  #   position = "bottomright",
  #   opacity = 1)
```

