---
date: 2018/1/23
output: rmarkdown::github_document
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output/") })
---

```{r, echo = FALSE}
knitr::opts_chunk$set (collapse=TRUE, comment="##", fig.path = "../images/")
```
  
> - unzip a folder containing a list of split data files  
> - read and merge individual files into one single data frame  
> - some exploratory analysis and visualizations  
  
data used: [Baby Names from Social Security Card Applications](https://catalog.data.gov/dataset/baby-names-from-social-security-card-applications-data-by-state-and-district-of-)  
  
code reference: [HERE](https://stat.ethz.ch/pipermail/r-help/2010-October/255593.html)  [HERE](https://stackoverflow.com/a/35236167)

***

```{r message=FALSE, warning=FALSE}
library (tidyverse); library (knitr); library (kableExtra) # Load the package
```
  
### Take a look at the folder containing the zip file
```{r}
list.files ("../data")
```
### Extract files from a zip archive and place them in a new folder
```{r}
path <- "../data/namesbystate/" 
unzip (zipfile = "./data/namesbystate.zip", # file to unzip
       exdir = path) # folder to deposit the files
```

### Now take a look at the folders
```{r echo=TRUE}
list.files ("../data")
list.files (path) # the one we just created
```
Note that the files are separated by states, and there is one pdf file in the folder, which we don't want  

### Files are ready. Prepare to read the files.
```{r}
files <- paste0 (path, list.files (path)) # produce a path for each file
files <- files [grep ("*TXT", files)] # Keep only the text files we want
head (read.table (files [1], sep = ",")) # without header
```

### Read through the file list and merge into one single data frame
```{r}
df <- do.call ("rbind", 
               lapply (files, read.table, sep = ",")) %>% 
  # rbindlist (lapply (files, read.table, sep = ",")) 
  # works as well
  as_tibble %>% # turn the table into tbl_df
  print

table (df$V1) # check if all states are in
 
header <- c ("state", "sex", "year", "name", "occurrence") # column names
names (df) <- header
df 
```

### Some exploratory analysis
```{r}
popular_names <- df %>% 
  group_by (state, sex, year) %>% 
  filter (occurrence == max (occurrence)) %>% 
  group_by (sex, year) %>% 
  summarize (name = names (which.max (table (name))))
  # get the most popular name of the year
  
popular_names %>% # print table
  spread (sex, name) %>% 
  kable (format = "markdown") %>% 
  print
```

### Use heatmap concept in ggplot2 to show time series changes
```{r, fig.width=10}
library (ggplot2)
ggplot (popular_names %>% filter (sex == "F"), 
       aes (x = year, y = reorder (name, -year), fill = name)) + 
  # reorder names according to their order of appearance (ascending year)
  # specify colors by names
  geom_tile () +
  labs (y = "most popular female names") +
  scale_x_continuous (breaks = seq (min (popular_names$year), max (popular_names$year), by = 10)) +
  theme (legend.position = "none") # remove legend

ggplot (popular_names %>% filter (sex == "M"), 
       aes (x = year, y = reorder (name, -year), fill = name)) +
  geom_tile () +
  labs (y = "most popular male names") +
    scale_x_continuous (breaks = seq (min (popular_names$year), max (popular_names$year), by = 10)) +
  theme (legend.position = "none")
```

