---
date: 2018/1/23
output: rmarkdown::github_document
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output/") })
---

```{r, echo = FALSE}
knitr::opts_chunk$set (collapse=TRUE, comment="##", fig.path = "../images/")
```
  
> - unzip a folder containing a list of split data files  
> - read and merge individual files into one single data frame  
> - some exploratory analysis and visualizations  
  
data used: [Baby Names from Social Security Card Applications](https://catalog.data.gov/dataset/baby-names-from-social-security-card-applications-data-by-state-and-district-of-)  
  
code reference: [HERE](https://stat.ethz.ch/pipermail/r-help/2010-October/255593.html)  [HERE](https://stackoverflow.com/a/35236167)

***

```{r message=FALSE, warning=FALSE}
library (tidyverse); library (knitr); library (kableExtra) # Load the package
```
  
### Take a look at the folder containing the zip file
```{r}
list.files ("../data")
```
### Extract files from a zip archive and place them in a new folder
```{r}
path <- "../data/namesbystate/" 
unzip (zipfile = "./data/namesbystate.zip", # file to unzip
       exdir = path) # folder to deposit the files
```

### Now take a look at the folders
```{r echo=TRUE}
list.files ("../data")
list.files (path) # the one we just created
```
Note that the files are separated by states, and there is one pdf file in the folder, which we don't want  

### Files are ready. Prepare to read the files.
```{r}
files <- paste0 (path, list.files (path)) # produce a path for each file
files <- files [grep ("*TXT", files)] # Keep only the text files we want
head (read.table (files [1], sep = ",")) # without header
```

### Read through the file list and merge into one single data frame
```{r}
df <- do.call ("rbind", 
               lapply (files, read.table, sep = ",")) %>% 
  # rbindlist (lapply (files, read.table, sep = ",")) 
  # works as well
  as_tibble %>% # turn the table into tibble
  print

table (df$V1) # check if all states are in
 
header <- c ("state", "sex", "year", "name", "occurrence") # column names
names (df) <- header
df 
```

### Some exploratory analysis: what are the most popular names of the years?
```{r}
national_count <- df %>% # sum up national count of baby names
  group_by(sex, year, name) %>% 
  summarize (occurrence_all = sum (occurrence)) %>% 
  arrange (sex, year, desc(occurrence_all)) %>% 
  print

popular_names <- national_count %>% # look for the most popular names
  filter (occurrence_all == max (occurrence_all)) 
  
popular_names %>% # print table
  spread (sex, name) %>% 
  kable (format = "markdown") %>% 
  print
```

### Use heatmap concept in ggplot2 to show time series changes
```{r popular_babynames, fig.width=10}
library (ggplot2)
ggplot (popular_names %>% filter (sex == "F"), 
       aes (x = year, y = reorder (name, -year), fill = name)) + 
  # reorder names according to their order of appearance (ascending year)
  # specify colors by names
  geom_tile () +
  labs (x = "", y="", title = "Most popular baby girl names") +
  scale_x_continuous (breaks = seq (min (popular_names$year), max (popular_names$year), by = 10)) +
  theme_minimal() +
  theme (legend.position = "none", # remove legend
         axis.text.y = element_text (size = 18))

ggplot (popular_names %>% filter (sex == "M"), 
       aes (x = year, y = reorder (name, -year), fill = name)) +
  geom_tile () +
  labs (x = "", y="", title = "Most popular baby boy names") +
  scale_x_continuous (breaks = seq (min (popular_names$year), max (popular_names$year), by = 10)) +
  theme_minimal() +
  theme (legend.position = "none", # remove legend
         axis.text.y = element_text (size = 18))
```
    
### Summary: 
1. Over the past century, the most popular female names have changed 10 times, whereas male names changed only 7 times, suggesting parents look for new names more frequently for baby girls than for boys.    
2. After the top position of the list was replaced by a new name, the old favorite names might come back once again in the following years. However, when the top position was replaced for the second time, the old favorites are no longer the favorites.    

##### Next questions: what social context caused the short appearance of Ashley and David?